### 2020-05-06 main.Rmd
updated the description on getting secreted non-effector data

Sequence data were collected from the PHI-Base database version 4.8 [@phibase] by accessing a text dump of the data kindly prepared on request by the team, the file can be accessed at [github.com/PHI-base/data](https://github.com/PHI-base/data/blob/master/releases/phi-base_current.csv). The pipeline in Figure \@ref(fig:effectorcollection) outlines the steps used. We filtered plant effector proteins and their taxonomic groups and collected sequences from UniProt Release `2019_05`, using the code in [github.com/TeamMacLean/ruth-effectors-prediction/](https://github.com/TeamMacLean/ruth-effectors-prediction/blob/master/scripts/r-scripts/getting-data-new/binary-class/0001_first_step_getting_data.Rmd). We created a correspondingly sized data set of non-effectors with secretion signals originating in species matched to those from which the effectors were drawn. We downloaded sequences for randomly selected proteins matching these criteria from Ensembl databases [Ensembl Fungi](https://fungi.ensembl.org/index.html) and [Ensembl Protists](https://protists.ensembl.org/index.html) manually using the BioMart tools. Since BioMart tool is not supported the Ensembl Bacteria, then we downloaded whole genome data matching the bacteria effector data from [Ensembl Bacteria](http://bacteria.ensembl.org/index.html) using the code in [github.com/TeamMacLean/ruth-effectors-prediction](https://github.com/TeamMacLean/ruth-effectors-prediction/blob/master/scripts/r-scripts/getting-secreted-data/0005_process_signalp_data.Rmd). Additionally, we used SignalP 3.0 in order to get the secreted sequences.

@@

Sequences for non-effector, secreted proteins were collected using a similar pipeline. Randomly selected proteins from each species carrying secretion signals were extracted from Ensembl databases using the BioMart tool. For each species noted in Tables \@ref(tab:bacefftable), \@ref(tab:fungiefftable) and \@ref(tab:oomefftable) we collected an identical number of non-effector, secreted proteins to that collected in the effector set. This gave us a balanced data set of effector proteins as positive learning examples and non-effector secreted proteins as negative learning examples.

>>>>

Sequence data were collected from the PHI-Base database version 4.8 [@phibase] by accessing a text dump of the data kindly prepared on request by the team, the file can be accessed at [github.com/PHI-base/data](https://github.com/PHI-base/data/blob/master/releases/phi-base_current.csv). The pipeline in Figure \@ref(fig:effectorcollection) outlines the steps used. We filtered plant effector proteins and their taxonomic groups and collected sequences from UniProt Release `2019_05`, using the code in [github.com/TeamMacLean/ruth-effectors-prediction/](https://github.com/TeamMacLean/ruth-effectors-prediction/blob/master/scripts/r-scripts/getting-data-new/binary-class/0001_first_step_getting_data.Rmd). We created a correspondingly sized data set of non-effectors with secretion signals originating in species matched to those from which the effectors were drawn. We downloaded sequences for randomly selected proteins matching these criteria from Ensembl databases [Ensembl Fungi](https://fungi.ensembl.org/index.html) and [Ensembl Protists](https://protists.ensembl.org/index.html) manually using the BioMart tools. Since BioMart tool is not supported the Ensembl Bacteria, then we downloaded whole genome data matching the bacteria effector data from [Ensembl Bacteria FTP](https://bacteria.ensembl.org/info/website/ftp/index.html) using the code in [github.com/TeamMacLean/ruth-effectors-prediction](https://github.com/TeamMacLean/ruth-effectors-prediction/blob/master/scripts/r-scripts/getting-secreted-data/0005_process_signalp_data.Rmd). Additionally, we used SignalP 3.0 in order to get the secreted sequences.

@@

Sequences for non-effector, secreted proteins were collected using a similar pipeline. Randomly selected proteins from each species carrying secretion signals were extracted from Ensembl databases using the BioMart tool. For each species noted in Tables \@ref(tab:bacefftable), \@ref(tab:fungiefftable) and \@ref(tab:oomefftable) we collected an identical number of non-effector, secreted proteins to that collected in the effector set. This gave us a balanced data set of effector proteins as positive learning examples and non-effector secreted proteins as negative learning examples. Figure \@ref(fig:noneffectorcollection) summaries the process of getting non-effector set. Using the gene information obtained from effector data, we downloaded secreted sequences from the same genome from each individual effector sequence depending on the availability of them in Ensembl Fungi and Ensembl Protists, otherwise we downloaded sequences from the same species as the individual effector using BioMart tool. However, BioMart tool is not supported for Ensembl Bacteria. Therefore, we downloaded the bacteria sequences using Ensmbl Bacteria FTP. Additionaly, we only selected the secreted sequences from prediction results of SignalP ran on the downloaded data. We then blast the combination of both secreted sequences data downloaded manually using BioMart tool and using Ensembl FTP with the effector sequence data, and removed identical sequences. This process is done in order to make sure there is no effector data in our candidate non-effector sample. Last step in this process then was to sample an identical number of non-effector data as in Tables \@ref(tab:bacefftable), \@ref(tab:fungiefftable) and \@ref(tab:oomefftable). In this step, we also blast every time we took a sample, so that there is no identical sequences within non-effector set.
